Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-13 index.Rmd
cleanup tool

@@

For the subset of events selected the High/Low EU index events (for the selected thresholds) have the abnormal returns below:

@@

```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = "EU.Index", width = "1000px")

checkboxInput("characteristic_irats_sign", "If you would like to change the sign of the firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]

  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(input$quantile_used)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)

feature_CALtable <- reactive({
   thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]

  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(input$quantile_used)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)

High_feature_Hedged_react <- reactive({
  thefeature = as.numeric(DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]])
  quantile_used <- as.numeric(input$quantile_used)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used)

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

<hr>
<hr>

@@

  thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
  thefeature1 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1[!is.na(thefeature1)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
  Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1[!is.na(thefeature1)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))

@@

  if (input$characteristic_irats2 != "None"){
    thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
    thefeature2 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
    High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2[!is.na(thefeature2)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
    Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2[!is.na(thefeature2)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
  }
  if (input$characteristic_irats3 != "None"){
    thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
    thefeature3 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats3)]]  
    High_feature_events3 = (scrub(thefeature3) >= quantile(thefeature3[!is.na(thefeature3)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
    Low_feature_events3 = (scrub(thefeature3) <= quantile(thefeature3[!is.na(thefeature3)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
  }
  if (input$characteristic_irats4 != "None"){
    thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
    thefeature4 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats4)]]  
    High_feature_events4 = (scrub(thefeature4) >= quantile(thefeature4[!is.na(thefeature4)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
    Low_feature_events4 = (scrub(thefeature4) <= quantile(thefeature4[!is.na(thefeature4)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
  }
  if (input$characteristic_irats5 != "None"){
    thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
    thefeature5 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats5)]]  
    High_feature_events5 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
    Low_feature_events5 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
  }
  if (input$characteristic_irats6 != "None"){
    thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
    thefeature6 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats6)]]  
    High_feature_events6 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
    Low_feature_events6 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
  }

>>>>

```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_single_analysis", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = "EU.Index", width = "1000px")

checkboxInput("characteristic_single_analysis_sign", "If you would like to change the sign of the firm characteristic (Low will be High and vice versa), select here:", value = FALSE, width = "1000px")

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)

High_feature_Hedged_react <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),1-quantile_used_ind)

Low_feature_Hedged_react <- reactive({
  thesign = ifelse(input$characteristic_single_analysis_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]
  thefeatureQ = thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_single_analysis)]]  
  quantile_used_ind = as.numeric(input$quantile_used)

  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeatureQ[!is.na(thefeatureQ)]),quantile_used_ind)

  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

For the subset of events selected the High/Low EU index events (for the selected EU thresholds below - you may need to change them depending on the sample of events used) have these abnormal returns:

@@

@@

  thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
  thefeature1 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
  thefeature1Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1Q[!is.na(thefeature1Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
  Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1Q[!is.na(thefeature1Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))

@@

  if (input$characteristic_irats2 != "None"){
    thesign = ifelse(input$characteristic_irats2_sign, -1, +1)
    thefeature2 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
    thefeature2Q = (thesign==-1) + thesign*BUYBACK_DATA_TOOL[[which(names(BUYBACK_DATA_TOOL) == input$characteristic_irats2)]]  
    High_feature_events2 = (scrub(thefeature2) >= quantile(thefeature2Q[!is.na(thefeature2Q)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
    Low_feature_events2 = (scrub(thefeature2) <= quantile(thefeature2Q[!is.na(thefeature2Q)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature2))
  }
  if (input$characteristic_irats3 != "None"){
    thesign = ifelse(input$characteristic_irats3_sign, -1, +1)
    thefeature3 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats3)]]  
    High_feature_events3 = (scrub(thefeature3) >= quantile(thefeature3[!is.na(thefeature3)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
    Low_feature_events3 = (scrub(thefeature3) <= quantile(thefeature3[!is.na(thefeature3)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature3))
  }
  if (input$characteristic_irats4 != "None"){
    thesign = ifelse(input$characteristic_irats4_sign, -1, +1)
    thefeature4 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats4)]]  
    High_feature_events4 = (scrub(thefeature4) >= quantile(thefeature4[!is.na(thefeature4)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
    Low_feature_events4 = (scrub(thefeature4) <= quantile(thefeature4[!is.na(thefeature4)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature4))
  }
  if (input$characteristic_irats5 != "None"){
    thesign = ifelse(input$characteristic_irats5_sign, -1, +1)
    thefeature5 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats5)]]  
    High_feature_events5 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
    Low_feature_events5 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
  }
  if (input$characteristic_irats6 != "None"){
    thesign = ifelse(input$characteristic_irats6_sign, -1, +1)
    thefeature6 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats6)]]  
    High_feature_events6 = (scrub(thefeature5) >= quantile(thefeature5[!is.na(thefeature5)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
    Low_feature_events6 = (scrub(thefeature5) <= quantile(thefeature5[!is.na(thefeature5)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature5))
  }
